|

### 2020-01-07 nontex/install/windows/fn_installations.Rmd
installation atom keymap, yiw and viwp
R4Econ package to REconTools Package

# Install my package, need to prepare package to work for ubuntu
# if install does not work, load locally
devtools::install_github("fanwangecon/R4Econ")

@@

@@

@@

>>>>

# Install my package, need to prepare package to work for ubuntu
# if install does not work, load locally
devtools::install_github("fanwangecon/REconTools")

@@

**Shortcuts**

- compile: *ctrl + alt + b*
- sync: *ctrl + alt + j*
- live save

@@

# latex-related
apm install language-latex
apm install latex

@@

Atom keymap.cson file:

```
# https://github.com/t9md/atom-vim-mode-plus/issues/130
'atom-text-editor.vim-mode-plus.insert-mode':
  'j j': 'vim-mode-plus:activate-normal-mode'
```
